Approximation as Differentiation notes

### 2025-03-13 notes/sec/grothendieck.tex
Think lambda-inv .famf needs to use both of the available .famf functions, combining them with copair.
Put new definition of lambda-inv in LaTeX.

\begin{enumerate}
\item $\idx{\lambda}_{X,Y,Z}$ is an isomorphism because $\idx{X} \times \idx{Y} \to \idx{Z} \iso \idx{X} \to
\idx{Y} \to \idx{Z}$. For $\faml{\lambda}_{X,Y,Z}$, define the following family of functions sending any
$(f,g): X \to [Y,Z]$ to $\lambda^{-1}_{X,Y,Z}(f,g) = (f^\dagger, g^\dagger): X \times Y \to Z$ with:
\begin{itemize}
\item $f^\dagger(x,y) = f'(y)$ where $f(x) = (f',g')$
\item $g^\dagger_{x,y} = g'_y \comp \proj_{\faml{Y}_y}$ where $f(x) = (f',g')$ and
$\proj_{\faml{Y}_y}: \faml{X}_x \biprod \faml{Y}_y \to \faml{Y}_y$
\end{itemize}

>>>>

\begin{enumerate}
\item Define the family of functions $\lambda^{-1}_{X,Y,Z}$ sending any $(f,g): X \to [Y,Z]$ to $(f^\dagger,
g^\dagger): X \times Y \to Z$ with:
\begin{itemize}
\item $f^\dagger(x,y) = f'(y)$
\item $g^\dagger_{x,y} = \coprodM{{\eval_{\prod}}_y \comp g_x}{g'_y}$
% $g'_y \comp \proj_{\faml{Y}_y}$ where $f(x) = (f',g')$ and $\proj_{\faml{Y}_y}: \faml{X}_x \biprod
% \faml{Y}_y \to \faml{Y}_y$
\end{itemize}
\noindent where $f(x) = (f',g')$.
